Self Regulation Ontology Retest Data Report

### 2017-03-20 SRO_Report.Rmd
working on new report

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
library(rmarkdown)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
options(digits = 4)
```

@@

```{r}
tmp = data.frame(persons=c(1,2,3,4,5,6),
                 rater1=c(9,6,8,7,10,6),
                 rater2=c(2,1,4,1,5,2),
                 rater3=c(5,3,6,2,6,4),
                 rater4=c(8,2,8,6,9,7))

ICC(tmp%>%select(-persons))

tmp = tmp %>% gather(rater,score,-persons)
tmp
summary(aov(score ~ rater+Error(factor(persons)), tmp))
```

```{r}
match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(time, score, -sub_id) %>%
    separate(time, c("dv","drop","time"), sep="[.]") %>%
    select(-drop)%>%
    mutate(time=ifelse(time=="x",1,2))
  return(df)
}

tmp = match_t1_t2("adaptive_n_back.mean_load") 
summary(aov(score~Error(sub_id)+time,tmp))
(0.692-((0.876*1+0.092*133)/134))/(0.692 + ((2-1)*((0.876*1+0.092*133)/134))) #ICC(1,1) ?
(0.692-0.092)/(0.692+ ((2-1)*0.092)+ ((2*(0.876-0.092))/134)) #ICC(2,1)
(0.692-0.092)/(0.692+((2-1)*0.092)) #ICC(3,1)
(0.692-((0.876*1+0.092*133)/134))/(0.692) #ICC(1,k)
(0.692-0.092)/(0.692+((2*(0.876-0.092))/134)) #ICC(2,k)
(0.692-0.092)/(0.692) #ICC(3.k)
sqrt((92.1+0.88+12.29)/133) #sd?
sd(tmp$score) #sd?
sqrt(0.092) #sem (smaller the better)
tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
ICC(tmp)

tmp = match_t1_t2("bis_bas_survey.BIS") 
summary(aov(score~Error(sub_id)+time,tmp))
# summary(aov(score~Error(sub_id/time)+time,tmp)) #same thing
sqrt(0.0477)
tmp = tmp %>% spread(time, score) %>% select(-dv, -sub_id)
ICC(tmp)
```

Based on Weir 2005 ICC(3,k) does not take in to account within subject differences between two time points (fixed effect/systematic error by time). Thus, it is well approximated by Pearson's r and subject to similar criticisms. So if you're going to use this you should at least that this effect is not significant for a measure.

Conclusion based on Weir:
get ICC(3,k)
report effect size of time (p value and partial eta squared)
get SEM (sqrt(MS_error))

```{r}
icc_df <- data.frame(icc = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  icc_df[numeric_cols[i], '...'] <- ...
}
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
library(rmarkdown)
library(psych)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
options(digits = 4)
```

@@

Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e. the fixed effect of time/systematic error). Thus, it is well approximated by Pearson's r and subject to similar criticisms. [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this effect size if one chooses to report with ICC(3,k). Based on his conclusions here I report:  
- ICC(3,k): ranges between 0-1; the larger the better  
- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time 
- SEM ($sqrt(MS_{error})$): standard error of measurement; the smaller the better

```{r}
match_t1_t2 <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(dv, score, -sub_id) %>%
    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
    select(-drop)
   return(df)
}

get_icc <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  df = df %>% spread(time, score) %>% select(-dv, -sub_id)
  icc = ICC(df)
  icc_3k = icc$results['Average_fixed_raters', 'ICC']
  return(icc_3k)
  }

get_eta <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ss_time = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq1',]
  ss_error = as.data.frame(unlist(mod$`Error: Within`))['Sum Sq2',]
  eta = ss_time/(ss_time+ss_error)
  return(eta)
  }

get_sem <- function(dv_var, t1_df = test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = match_t1_t2(dv_var, t1_df = t1_df, t2_df = t2_df, merge_var = merge_var)
  mod = summary(aov(score~Error(sub_id)+time, df))
  ms_error = as.data.frame(unlist(mod$`Error: Within`))['Mean Sq2',]
  sem = sqrt(ms_error)
  return(sem)
}
```

```{r}
icc_df <- data.frame(icc = rep(NA, length(numeric_cols)), 
                     eta_sq = rep(NA, length(numeric_cols)),
                     sem = rep(NA, length(numeric_cols)))

@@

for(i in 1:length(numeric_cols)){
  icc_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  icc_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  icc_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
}
```

Add column to tasks vs. surveys in icc table

```{r}
icc_df$dv = row.names(icc_df)
row.names(icc_df) = seq(1:nrow(icc_df))
icc_df$task = 'task'
icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
icc_df
```

### Distributions of ICC's by task vs. survey

Survey reliabilities are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE}
icc_df %>%
  gather(key,value,-dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(position = 'stack', alpha=0.5)+
  theme_bw()+
  facet_wrap(~key,scales='free')
```

Median reliability and the number of variables for both the surveys and the tasks
```{r}
icc_df %>%
  group_by(task) %>%
  summarise(median_icc = median(icc),
            median_eta_sq = median(eta_sq),
            median_sem = median(sem),
            num_vars = n())
```
